\chapter{Administration Manual - SAP Business One ServiceLayer Proxy with Database Connector}
\label{attachments:admin-manual-sap}
This manual outlines the deployment and administration procedures for the SAP Business One ServiceLayer Proxy integrated with a database connector. 
Details how to establish and manage the service within a Docker environment, using Nginx as a reverse proxy and Certbot for SSL certificate management. 
The following sections will guide you through the necessary steps to configure and maintain the system effectively, ensuring secure and optimal operation.

\section{Prerequisites}
Before proceeding with the installation of SAP Business One ServiceLayer Proxy, it is important to ensure that the deployment node meets the necessary requirements.
Both the SAP ServiceLayer service and the Microsoft SQL database should be reachable from the server network if not exposed publicly.
However, it is worth noting that, in order to minimise communication latency, it is good to keep the servers geographically and network-wise as close as possible. 

Please, note that the deployment node of the Proxy should be reachable from public network.
Ideally, there should be a domain name routed to the server.

The minimal system requirements of the service come primarily from the requirements of the Docker environment.
For more information on Docker installation and requirements, please refer to the official Docker documentation \url{https://docs.docker.com/}.
For the containers Ngninx and Certbot, we will ideally need at least 5GB of free space.

\section{Deployment}
\label{sec:admin-manual-sap.deployment}
The deployment node is a \ac{VPS} hosted locally within the company.
The server is running Ubuntu Server 22.04.3 with Docker version 24.0.7.

\subsection{PostgreSQL database}
Utilised PostgreSQL database container is the official image of PostgreSQL version 16.0 (\texttt{postgres:16.0}).

\subsection{Proxy Service}
The service container is automatically built as a private image on Docker Hub \texttt{michalpulpan/milpex-sap-api:latest}.

\subsubsection{Environment variables}
To ensure both SAP ServiceLayer and MS SQL connections, it is necessary to run the service with a set of environment variables located in \texttt{/srv/sap-api/\.env}
\begin{lstlisting}[language=bash,caption={SAP Business One ServiceLayer Proxy with database connector environment variables setup}]
DB_HOST=postgres_host
DB_PORT=postgres_port
DB_USERNAME=postgres_username
DB_PASSWORD=postgres_password

APP_DOMAIN=production_platform_url

SAP_SERVICE_LAYER_URL=https://SAP_URL:PORT/b1s/v1
SAP_SERVICE_LAYER_PROD_USERNAME=sap_prod_username
SAP_SERVICE_LAYER_PROD_PASSWORD=sap_prod_password
SAP_SERVICE_LAYER_PROD_DB=sap_prod_db
SAP_SERVICE_LAYER_DEV_USERNAME=sap_dev_username
SAP_SERVICE_LAYER_DEV_PASSWORD=sap_dev_password
SAP_SERVICE_LAYER_DEV_DB=SBO-sap_dev_db

MSSQL_DEV_DB=mssql_dev_db
MSSQL_DEV_DB_USERNAME=mssql_dev_username
MSSQL_DEV_DB_PASSWORD=mssql_dev_password
MSSQL_DEV_DB_HOST=mssql_dev_host
MSSQL_DEV_DB_PORT=mssql_dev_post

MSSQL_PROD_DB=mssql_prod_db
MSSQL_PROD_DB_USERNAME=mssql_prod_username
MSSQL_PROD_DB_PASSWORD=mssql_prod_password
MSSQL_PROD_DB_HOST=mssql_prod_host
MSSQL_PROD_DB_PORT=mssql_prod_port
\end{lstlisting}


\section{Docker Compose}
In order to orchestrate and simplify the deployment process of both services, it is recommended to use the Docker Compose tool.
The \texttt{docker-compose.yml} configuration on the deployment node \ref{sec:admin-manual-sap.deployment} is specified in \texttt{/srv/sap-api}.
The example \texttt{docker-compose.yml} is:
\begin{lstlisting}[caption={SAP Business One ServiceLayer Proxy with database connector \texttt{docker-compose.yml}}]
version: '3.9'

services:
  api:
    container_name: sapb1-middleware-api
    image: michalpulpan/milpex-sap-api:latest
    ports:
      - '3333:3000'
    depends_on:
      - database
    env_file:
      - .env
    profiles:
      - prod
    restart: always
    logging:
      driver: json-file
      options:
        max-size: "5m"
        max-file: "10"
  database:
    container_name: sapb1-middleware-postgres-database
    command: postgres -c 'max_connections=300'
    environment:
      POSTGRES_USER: postgres
      POSTGRES_PASSWORD: postgres
      POSTGRES_DB: postgres
    restart: always
    image: postgres:16.0
    volumes:
      - database_volume:/var/lib/postgresql/data:Z
    ports:
      - '5432:5432'
    profiles:
      - prod
volumes:
  database_volume:
    name: database_volume
    external: true
\end{lstlisting}

\subsection{\texttt{Watchtower}}
\texttt{Watchtower} is used to pull and rerun newly build images on the Docker Hub.
The \texttt{Watchtower} is ran as a docker container from a Compose file specified in \texttt{/srv/monitoring/docker-compose.yml}.

\begin{lstlisting}[caption={Watchtower \texttt{docker-compose.yml}}]
version: '3.9'
services:
  watchtower:
    image: containrrr/watchtower
    restart: always
    env_file:
      - watchtower/.env
    volumes:
      - /home/user/.docker/config.json:/config.json
      - /var/run/docker.sock:/var/run/docker.sock
\end{lstlisting}

\texttt{Watchtower} is defined to automatically send Slack notifications using notification library named \texttt{shoutrrr} \url{https://containrrr.dev/projects/shoutrrr/} module when new version is pulled. The Slack notification is defined in the \texttt{.env} file located in \texttt{/srv/monitoring/watchtower/}:
\begin{lstlisting}[caption={Watchtower environment variables}]
WATCHTOWER_LABEL_ENABLE=1
WATCHTOWER_NOTIFICATIONS="shoutrrr"
WATCHTOWER_NOTIFICATION_URL="slack://token:token@channel/"
\end{lstlisting}
In order to define other communication channel, please refer to the \texttt{shoutrrr} documentation \url{https://containrrr.dev/projects/shoutrrr/}

\subsection{Working with the containers}
To start/stop or update containers, it is recommended to use Docker Compose.
\subsubsection{Start the containers}
In order to start the containers in background, go to the folder \texttt{/srv/sap-api} and run \texttt{docker compose --profile prod up -d}

\subsubsection{Stop the containers}
In order to stop the containers in background, go to the folder \texttt{/srv/sap-api} and run \texttt{docker compose stop}

\subsubsection{Update the service}
In order to update the API service, go to the folder \texttt{/srv/sap-api} and run \texttt{docker compose pull api \&\& docker compose up --profile prod -d}.
The specified command will pull the latest container from the Docker Hub and start the services again.

However, note that containers should update automatically if there is a new image.

\section{Reverse-proxy}
A reverse-proxy used for deployment is Nginx version 1.18.0.
Since there is a domain routed directly onto the server, we can use Nginx for internal routing as a reverse-proxy.

The standard Nginx definition is found by convention in \texttt{sites-available} within the Nginx specific folder \texttt{/etc/nginx}.
The route is then symlinked to the \texttt{/etc/nginx/sites-enabled} folder using the following command:
\begin{lstlisting}[caption={Command to create symbolic link by Nginx convention}]
sudo ln -s /etc/nginx/sites-available/domain /etc/nginx/sites-enabled/
\end{lstlisting}

\subsection{SSL certificate}
For automatically SSL certificate renewal from Let's Encrypt, \texttt{Certbot} was installed and configured.
To obtain a certificate for the newly created route, run:
\begin{lstlisting}[caption={Certbot command to obtain SSL certificate}]
sudo certbot --nginx -d example.com -d www.example.com
\end{lstlisting}






