\chapter{Administration Manual - \texttt{Data-sender}}
\label{attachments:admin-manual-data-sender}

In this manual will be described the deployment process of the \texttt{Data-sender} between the platform and SAP ServiceLayer Proxy.
The deployment process contains running the service in a Docker environment in scheduled mode.

\section{Prerequisites}
Before proceeding with the installation of \texttt{Data-sender}, it is important to ensure that the deployment node meets the necessary requirements.
Both the public API of the platform and the SAP ServiceLayer Proxy should be accessible from the server network if not exposed publicly.
However, it is worth noting that, in order to minimise communication latency, it is good to keep the servers geographically and network-wise as close as possible. 

The minimal system requirements of the service come primarily from the requirements of the Docker environment.
For more information on Docker installation and requirements, please refer to the official Docker documentation \url{https://docs.docker.com/}.

\section{Deployment}
\label{sec:admin-manual-sap.deployment}
The deployment node is a \ac{VPS} hosted locally within the company.
The server is running Ubuntu Server 22.04.3 with Docker version 24.0.7.

\subsection{\texttt{Data-sender} service}
The service container is automatically built as a private image in the Docker Hub \texttt{michalpulpan/milpex-sap-data-sender:latest}.

\subsubsection{Environment variables}
To ensure the connection to the SAP ServiceLayer Proxy and the platform, it is necessary to run the service with a set of environment variables located in \texttt{\/srv\/sap-api/.data\_sender.env} in Listings \ref{attachment:data-sender-admin.listings-evn}.

\begin{lstlisting}[language=bash,caption={Data sender environment configuration}]
ENVIRONMENT=production

SAP_PROXY_BASE_URL=https://api.company.com
SAP_PROXY_USERNAME=username
SAP_PROXY_PASSWORD=password


PARCELSYNC_BASE_URL=https://api.parcelsync.io
PARCELSYNC_API_KEY=key
\end{lstlisting}
\label{attachment:data-sender-admin.listings-evn}


\section{Docker Compose}
In order to orchestrate and simplify the deployment process of both services, it is recommended to use the Docker Compose tool.
The \texttt{docker-compose.yml} configuration on the deployment node \ref{sec:admin-manual-sap.deployment} is specified in \texttt{/srv/sap-api/} directory.

The example \texttt{docker-compose.yml} is in Listings \ref{attachment:data-sender-admin.listings-dockercompose}.
\begin{lstlisting}[caption={Data-sender \texttt{docker-compose.yml}}]
version: '3.9'

services:
  data-sender:
    container_name: sapb1-data-sender
    image: michalpulpan/milpex-sap-data-sender:latest
    env_file:
      - .data_sender.env
    depends_on:
      - api
    restart: always
    profiles:
      - prod
    logging:
      driver: json-file
      options:
        max-size: "5m"
        max-file: "10"

\end{lstlisting}
\label{attachment:data-sender-admin.listings-dockercompose}
\subsection{\texttt{Watchtower}}
\texttt{Watchtower} is used to pull and rerun newly build images on the Docker Hub.
The \texttt{Watchtower} is ran as a docker container from a Compose file specified in \texttt{/srv/monitoring/docker-compose.yml} in Listings \ref{attachment:data-sender-admin.listings-dockercompose.watchtower}.

\begin{lstlisting}[caption={Watchtower \texttt{docker-compose.yml}}]
version: '3.9'
services:
  watchtower:
    image: containrrr/watchtower
    restart: always
    env_file:
      - watchtower/.env
    volumes:
      - /home/user/.docker/config.json:/config.json
      - /var/run/docker.sock:/var/run/docker.sock
\end{lstlisting}
\label{attachment:data-sender-admin.listings-dockercompose.watchtower}

\texttt{Watchtower} is defined to automatically send Slack notifications using notification library named \texttt{shoutrrr} \url{https://containrrr.dev/projects/shoutrrr/} module when new version is pulled. The Slack notification is defined in the \texttt{.env} file located in \texttt{/srv/monitoring/watchtower/}:
\begin{lstlisting}[caption={Watchtower environment variables}]
WATCHTOWER_LABEL_ENABLE=1
WATCHTOWER_NOTIFICATIONS="shoutrrr"
WATCHTOWER_NOTIFICATION_URL="slack://token:token@channel/"
\end{lstlisting}
In order to define other communication channel, please refer to the \texttt{shoutrrr} documentation \url{https://containrrr.dev/projects/shoutrrr/}

\subsection{Working with the containers}
To start/stop or update containers, it is recommended to use Docker Compose.
\subsubsection{Start the containers}
In order to start the containers in background, go to the folder \texttt{/srv/sap-api} and run \texttt{docker compose --profile prod up -d}

\subsubsection{Stop the containers}
In order to stop the containers in background, go to the folder \texttt{/srv/sap-api} and run \texttt{docker compose stop}

\subsubsection{Update the service}
In order to update the API service, go to the folder \texttt{/srv/sap-api} and run \texttt{docker compose pull api \&\& docker compose up --profile prod -d}.
The specified command will pull the latest container from the Docker Hub and start the services again.
Note that containers should update automatically 
within few minutes if there is a new image.



